---
title: "Dataframe Question"
author: 
  name: 'Quentin Goss `quentingoss0323@floridapoly.edu`'
  affiliation: "Florida Polytechnic University `COP5090.01`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_notebook
---

I have the following data.
```{r}
load('coords.clusters.RData')
```

It is the result of using the `kmeans` function. We can view the data but right now I only care about one part, `$size`, which is the information about how many nodes are in a cluster.  Cluster 1 has 46 nodes, cluster 2 has 70 items and so on...

```{r}
coords.clusters$size
```

I want to preload this as a datastructure into memory with `NA` values that I can later replace with `character` values. I can determine the length of `$size` with the length function, so I know how many rows that I want in this data structure.

```{r}
length(coords.clusters$size)
```

When I use the `summary` function on my `coords.clusters` dataframe I see this:
```{r}
summary(coords.clusters)
```

To better explain what I want, here is a summary of how I'd like my data structure to look like: 

```
          Length Class  Mode
cluster_1   42   -none- character
cluster_2   70   -none- character
cluster_3   73   -none- character
cluster_4   81   -none- character
cluster_5   45   -none- character
cluster_6   42   -none- character
cluster_7   55   -none- character
```

And so, my question is **How do I create a data frame where** `nrow = length(coords.clusters$size)` **and** `ncol = coords.clusters$size[i]` **and** `rownames(mydf) <- cluster_i` **and every value is set to** `NA` **?**

#### Preliminary Answer

According to the descriptions above, to create this data frame

```
          Length Class  Mode
cluster_1   42   -none- character
cluster_2   70   -none- character
cluster_3   73   -none- character
cluster_4   81   -none- character
cluster_5   45   -none- character
cluster_6   42   -none- character
cluster_7   55   -none- character
```

we could do 

```{r}
nn <- length(coords.clusters$size)
```


```{r}
# first two columns of data frame
cl_number <- 1:nn
cl_size <- coords.clusters$size
```

Create data frame

```{r}
# using items, qclass, qmode to avoid confusion 
# with lenght, class, and mode functions
df_1 <- data.frame(cluster = cl_number, items = cl_size, 
           qclass = rep(NA_character_, nn), qmode = character(nn))

df_1
```

```{r}
summary(df_1)
```

if you really want the data frame to have _rownames_ (there are reasons why I do not necessarily follow that approach), you can just do

```{r}
# create row names
cl_rownames <- paste0(rep("cluster_", nn), 1:nn)
cl_rownames
```


```{r}
# dataframe with row names
df_2 <- data.frame(items = cl_size, 
           qclass = rep(NA_character_, nn), qmode = character(nn))
row.names(df_2) <- cl_rownames
```

```{r}
# this is how it looks now
df_2
```


Also, a good tool to check when working with models in R (lm, kmeans, etc) is the `broom` [package](https://cran.r-project.org/web/packages/broom/). It allows you to get _tidy outputs_ from the models. 

For your interest, since you're working with `kmeans()`, the following vignette might be useful:

<https://cran.r-project.org/web/packages/broom/vignettes/kmeans.html>