---
title: "Quentin K-Means questions"
output: html_notebook
---

We have an R object named `xynames`.
```{r}
load('xynames.RData')
```

Within the data structure `xynames` are three lists that contain all the data needed to create a plot.
```{r}
names(xynames) <- c('x','y','name')
summary(xynames)
```

We can plot them abd see what the plot looks like.
```{r}
coords.x <- unlist(xynames[1])
coords.y <- unlist(xynames[2])
coords.names <- unlist(xynames[3])
plot(
  x = coords.x,
  y = coords.y
)
```

We want to try out the `kmeans` method in base R, so we create a data structure that `kmeans` accepts.
```{r}
coords.matrix <- rbind(
  matrix(coords.x,ncol=2),
  matrix(coords.y,ncol=2)
)
colnames(coords.matrix) <- c('x','y')
rownames(coords.matrix) <- coords.names
print(head(coords.matrix,n=10L))
```

And then we run them through the `kmeans` method.
```{r}
ncenters <- 7
coords.clusters <- kmeans(
  x = coords.matrix,
  centers = ncenters,
  iter.max = 50,
  nstart = 27,
  algorithm = 'Hartigan-Wong'
)
print(coords.clusters)
```

We can view our clusters with a plot.
```{r}
plot(x = coords.matrix, col = coords.clusters$cluster)
points(coords.clusters$centers, col = 1:ncenters , pch = 8, cex = 2)
```

I can see that my junctions (points) are being clustered when I plot my points color coded to the clusters they belong with. 
```{r}
#png(filename='../../exports/bloopers/leopard.blooper.png', width = 640, height = 480, units='px')
plot(
  x = coords.x,
  y = coords.y,
  col = coords.clusters$cluster
)
points(coords.clusters$centers, col = 1:ncenters , pch = 8, cex = 2)
```

