---
title: "Dataframe Question"
author: 
  name: 'Quentin Goss `quentingoss0323@floridapoly.edu`'
  affiliation: "Florida Polytechnic University `COP5090.01`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_notebook
---

I have the following data.
```{r}
load('coords.clusters.RData')
```

It is the result of using the `kmeans` function. We can view the data but right now I only care about one part, `$size`, which is the information about how many nodes are in a cluster.  Cluster 1 has 46 nodes, cluster 2 has 70 items and so on...
```{r}
coords.clusters$size
```

I want to preload this as a datastructure into memory with `NA` values that I can later replace with `character` values. I can determine the length of `$size` with the length function, so I know how many rows that I want in this data structure.
```{r}
length(coords.clusters$size)
```

When I use the `summary` function on my `coords.clusters` dataframe I see this:
```{r}
summary(coords.clusters)
```

To better explain what I want, here is a summary of how I'd like my data structure to look like: 
```
          Length Class  Mode
cluster_1   42   -none- character
cluster_2   70   -none- character
cluster_3   73   -none- character
cluster_4   81   -none- character
cluster_5   45   -none- character
cluster_6   42   -none- character
cluster_7   55   -none- character
```

And so, my question is **How do I create a data frame where** `nrow = length(coords.clusters$size)` **and** `ncol = coords.clusters$size[i]` **and** `rownames(mydf) <- cluster_i` **and every value is set to** `NA` **?**
